Frame X Amici Frequencies by Case

### 2022-05-17 eda/abortion-cases-frames-plots.Rmd
frame freq by case for eda

---
title: "abortion cases"
author: "Amanda Konet"
date: "`r date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, error = F)
library(tidyverse)
library(ggplot2)
library(boxr)
box_auth()
```

```{r}
df <- box_read("949904531983", read_fun = readr::read_csv)
```

# Abortion Negative II

```{r}
df %>% 
  select(case, ddate2, ) %>% 
  mutate(title = "Word/Phrase Count for Abortion Negative II Frame",
         year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, decision_date), y = anii_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Abortion Negative II Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

# actor_couple

```{r}
dec_frames %>% 
  select(case, decision_date, ac_freq) %>% 
  mutate(title = "Word/Phrase Count for Actor Couple Frame",
         year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = ac_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Actor Couple Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

# actor_fetus

```{r}
dec_frames %>% 
  select(case, decision_date, af_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = af_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Actor Fetus Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

# actor_physician

```{r}
dec_frames %>% 
  select(case, decision_date, ap_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = ap_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Actor Physician Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

# compulsoryII

```{r}
dec_frames %>% 
  select(case, decision_date, c2_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = c2_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Compulsory II Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

# compulsoryMotherhood

```{r}
dec_frames %>% 
  select(case, decision_date, cm_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = cm_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Compulsory Motherhood Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

# favorChildbirth

```{r}
dec_frames %>% 
  select(case, decision_date, fc_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = fc_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Favor Childbirth Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

# health

```{r}
dec_frames %>% 
  select(case, decision_date, he_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = he_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Health Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

# intersectionality

```{r}
dec_frames %>% 
  select(case, decision_date, in_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = in_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Intersectionality Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

# morality

>>>>

---
title: "Frame X Amici Frequencies by Case"
author: "Amanda Konet"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, error = F)
library(tidyverse)
library(ggplot2)
library(boxr)
box_auth()
final_cases <- "949901868853"
```

```{r}
# data is 1 row per justice vote; convert to 1 row per case
df <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  filter(case != "Gonzales v PP") %>% 
  mutate(across(c(forgauf_abortion_different:forgauf_womens_rights,
                  legauf_abortion_different:legauo_womens_rights,
                  lifauo_abortion_different:medauo_womens_rights,
                  relauf_abortion_different:relauo_womens_rights),
                ~replace_na(.x, 0))) %>% 
  distinct(case, ddate2,
           forgauf_privacy, forgauf_undue_burden, forgauf_womens_health, forgauf_evidence,
           medauf_womens_future_life, medauf_womens_health,
           lifauo_undue_burden,
           relauo_undue_burden, relauo_abortion_regret, relauo_fetus,
           medauo_final_authority, medauo_evidence, medauo_morality_religion) %>% 
  mutate(case = case_when(
    case == "Anders v Floyd" ~ "Anders",
    case == "Ayotte v PP" ~ "Ayotte",
    case == "Beal v Doe" ~ "Beal",
    case == "Bellotti v Baird 1976" ~ "Bellotti 76",
    case == "Bellotti v Baird 1979" ~ "Bellotti 79",
    case == "Bigelow v Virginia" ~ "Bigelow",
    case == "Bray v Alexandria Womens Health Clinic" ~ "Bray",
    case == "City of Akron v Akron Center" ~ "City of Akron",
    case == "Colautti v Franklin" ~ "Colautti",
    case == "Diamond v Charles" ~ "Diamond",
    case == "Doe v Bolton" ~ "Bolton",
    case == "Frisby v Schultz" ~ "Frisby",
    case == "Gonzales v Carhart" ~ "Gonzales",
    case == "H.L. v Matheson" ~ "H.L.",
    case == "Harris v McRae" ~ "Harris",
    case == "Hill v Colorado" ~ "Hill",
    case == "Hodgson v Minnesota" ~ "Hodgson",
    case == "Scheidler v NOW 2003" ~ "Scheidler 03",
    case == "Scheidler v Now 2006" ~ "Scheidler 06",
    case == "Madsen v Womens Health Center" ~ "Madsen",
    case == "June v Russo" ~ "June",
    case == "Maher v Roe" ~ "Maher",
    case == "McCullen v Coakley" ~ "McCullen",
    case == "NOW v Scheidler 1994" ~ "Scheidler 94",
    case == "Ohio v Akron Center" ~ "Ohio",
    case == "PP v Ashcroft" ~ "Ashcroft",
    case == "PP v Danforth" ~ "Danforth",
    case == "PP v Casey" ~ "Casey",
    case == "Poelker v Doe" ~ "Poelker",
    case == "Roe v Wade" ~ "Roe",
    case == "Rust v Sullivan" ~ "Rust",
    case == "Schenck v Pro-Choice Network" ~ "Schenck",
    case == "Simopoulos v Virginia" ~ "Simopoulos",
    case == "Singleton v Wulff" ~ "Singleton",
    case == "Stenberg v Carhart" ~ "Stenberg",
    case == "Thornburgh v American College of OBGYNs" ~ "Thornburgh",
    case == "United States v Vuitch" ~ "Vuitch",
    case == "Webster v Reproductive Health Services" ~ "Webster",
    case == "WWH v Hellerstedt" ~ "WWH",
    case == "Williams v Zbaraz" ~ "Williams",
    T ~ case
  ))
```

# Cases

```{r, eval=F, echo=T}
case == "Anders v Floyd" ~ "Anders",
case == "Ayotte v PP" ~ "Ayotte",
case == "Beal v Doe" ~ "Beal",
case == "Bellotti v Baird 1976" ~ "Bellotti 76",
case == "Bellotti v Baird 1979" ~ "Bellotti 79",
case == "Bigelow v Virginia" ~ "Bigelow",
case == "Bray v Alexandria Womens Health Clinic" ~ "Bray",
case == "City of Akron v Akron Center" ~ "City of Akron",
case == "Colautti v Franklin" ~ "Colautti",
case == "Diamond v Charles" ~ "Diamond",
case == "Doe v Bolton" ~ "Bolton",
case == "Frisby v Schultz" ~ "Frisby",
case == "Gonzales v Carhart" ~ "Gonzales",
case == "H.L. v Matheson" ~ "H.L.",
case == "Harris v McRae" ~ "Harris",
case == "Hill v Colorado" ~ "Hill",
case == "Hodgson v Minnesota" ~ "Hodgson",
case == "Scheidler v NOW 2003" ~ "Scheidler 03",
case == "Scheidler v Now 2006" ~ "Scheidler 06",
case == "Madsen v Womens Health Center" ~ "Madsen",
case == "June v Russo" ~ "June",
case == "Maher v Roe" ~ "Maher",
case == "McCullen v Coakley" ~ "McCullen",
case == "NOW v Scheidler 1994" ~ "Scheidler 94",
case == "Ohio v Akron Center" ~ "Ohio",
case == "PP v Ashcroft" ~ "Ashcroft",
case == "PP v Danforth" ~ "Danforth",
case == "PP v Casey" ~ "Casey",
case == "Poelker v Doe" ~ "Poelker",
case == "Roe v Wade" ~ "Roe",
case == "Rust v Sullivan" ~ "Rust",
case == "Schenck v Pro-Choice Network" ~ "Schenck",
case == "Simopoulos v Virginia" ~ "Simopoulos",
case == "Singleton v Wulff" ~ "Singleton",
case == "Stenberg v Carhart" ~ "Stenberg",
case == "Thornburgh v American College of OBGYNs" ~ "Thornburgh",
case == "United States v Vuitch" ~ "Vuitch",
case == "Webster v Reproductive Health Services" ~ "Webster",
case == "WWH v Hellerstedt" ~ "WWH",
case == "Williams v Zbaraz" ~ "Williams"
```

@@

# Reproductive Rights

## Forgauf & Privacy

```{r}
df %>% 
  select(case, ddate2, forgauf_privacy) %>% 
  mutate(year = lubridate::year(ddate2)) %>% 
  ggplot(., aes(x = reorder(case, ddate2), y = forgauf_privacy)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
    title = "Word/Phrase Count for FORG Privacy Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "gray10", size = 7.4, angle = 45),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "gray45", size = 7.4, angle = 90, vjust = 0.5, hjust=1),
    axis.text.y = element_text(color = "gray45", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

## Forgauf & Undue Burden

```{r}
df %>% 
  select(case, ddate2, forgauf_undue_burden) %>% 
  mutate(year = lubridate::year(ddate2)) %>% 
  ggplot(., aes(x = reorder(case, ddate2), y = forgauf_undue_burden)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
    title = "Word/Phrase Count for FORG Undue Burden Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "gray10", size = 7.4, angle = 45),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "gray45", size = 7.4, angle = 90, vjust = 0.5, hjust=1),
    axis.text.y = element_text(color = "gray45", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

## Medauf & Women's Futures

```{r}
df %>% 
  select(case, ddate2, medauf_womens_future_life) %>% 
  mutate(year = lubridate::year(ddate2)) %>% 
  ggplot(., aes(x = reorder(case, ddate2), y = medauf_womens_future_life)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
    title = "Word/Phrase Count for RR Med Women's Futures Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "gray10", size = 7.4, angle = 45),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "gray45", size = 7.4, angle = 90, vjust = 0.5, hjust=1),
    axis.text.y = element_text(color = "gray45", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

## Forgauf & Women's Health

```{r}
df %>% 
  select(case, ddate2, forgauf_womens_health) %>% 
  mutate(year = lubridate::year(ddate2)) %>% 
  ggplot(., aes(x = reorder(case, ddate2), y = forgauf_womens_health)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
    title = "Word/Phrase Count for FORG Women's Health Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "gray10", size = 7.4, angle = 45),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "gray45", size = 7.4, angle = 90, vjust = 0.5, hjust=1),
    axis.text.y = element_text(color = "gray45", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

## Medauf & Women's Health

```{r}
df %>% 
  select(case, ddate2, medauf_womens_health) %>% 
  mutate(year = lubridate::year(ddate2)) %>% 
  ggplot(., aes(x = reorder(case, ddate2), y = medauf_womens_health)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
    title = "Word/Phrase Count for RR Med Women's Health Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "gray10", size = 7.4, angle = 45),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "gray45", size = 7.4, angle = 90, vjust = 0.5, hjust=1),
    axis.text.y = element_text(color = "gray45", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

## Forgauf & Expert Evidence

```{r}
df %>% 
  select(case, ddate2, forgauf_evidence) %>% 
  mutate(year = lubridate::year(ddate2)) %>% 
  ggplot(., aes(x = reorder(case, ddate2), y = forgauf_evidence)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
    title = "Word/Phrase Count for FORG Expert Evidence Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "gray10", size = 7.4, angle = 45),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "gray45", size = 7.4, angle = 90, vjust = 0.5, hjust=1),
    axis.text.y = element_text(color = "gray45", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

# Antiabortion

## Lifauo & Undue Burden

```{r}
df %>% 
  select(case, ddate2, lifauo_undue_burden) %>% 
  mutate(year = lubridate::year(ddate2),
         ) %>% 
  ggplot(., aes(x = reorder(case, ddate2), y = lifauo_undue_burden)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
    title = "Word/Phrase Count for Antiabortion Undue Burden Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "gray10", size = 7.4, angle = 45),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "gray45", size = 7.4, angle = 90, vjust = 0.5, hjust=1),
    axis.text.y = element_text(color = "gray45", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

## Relauo & Undue Burden

```{r}
df %>% 
  select(case, ddate2, relauo_undue_burden) %>% 
  mutate(year = lubridate::year(ddate2)) %>% 
  ggplot(., aes(x = reorder(case, ddate2), y = relauo_undue_burden)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
    title = "Word/Phrase Count for AA Rel Undue Burden Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "gray10", size = 7.4, angle = 45),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "gray45", size = 7.4, angle = 90, vjust = 0.5, hjust=1),
    axis.text.y = element_text(color = "gray45", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

@@

## Medauo & Final Authority

```{r}
df %>% 
  select(case, ddate2, medauo_final_authority) %>% 
  mutate(year = lubridate::year(ddate2)) %>% 
  ggplot(., aes(x = reorder(case, ddate2), y = medauo_final_authority)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
    title = "Word/Phrase Count for AA Med Final Authority Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "gray10", size = 7.4, angle = 45),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "gray45", size = 7.4, angle = 90, vjust = 0.5, hjust=1),
    axis.text.y = element_text(color = "gray45", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```
